---
title: "barPLots"
format: html
---

Run second_foray_lowpass first

```{r}
#| include: false
library(tidyverse)
library(tidymodels)
```

```{r}
all_data %>% 
  ggplot(aes(x = language)) +
  geom_bar()
```


```{r}
all_data <- all_data %>% 
  mutate(
    tone_contour = as.factor(tone_contour)
  )
```


```{r}
jjSplit <- all_data %>% 
  mutate(
    jj = case_when(
      language == "Yi" ~ TRUE,
      language == "Bo" ~ TRUE,
      language == "Luchun" ~ TRUE,
      .default = FALSE
    )
  )
```


This is just trying to get the same stuff as the JJ paper. We are seeing very similar behavior with our V1 as their PC1, but not really after that.
```{r}
all_data %>% 
  # filter(language == "Yi" | language == "Bo" | language == "Luchun") %>%
  ggplot(aes(x = phonation, y = PC4)) +
  stat_summary(fun = "mean", geom = "bar", fill = "skyblue", color = "black") +
  geom_hline(yintercept = 0) +
  stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1), geom = "errorbar", width = 0.2)

all_data %>% 
  ggplot(aes(x = PC2, y = Phonation, color = Phonation)) +
  geom_boxplot() +
  facet_wrap(~language)
```

```{r}
jjSplit %>% 
  ggplot(aes(x = jj, y = V2)) +
  stat_summary(fun = "mean", geom = "bar", fill = "skyblue", color = "black") +
  stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1),
               geom = "errorbar", width = 0.2)
# check if above is stat. sig.
jjSplitCraszy <- lmspec %>% 
  fit(V2 ~ jj, data = jjSplit)
jjSplitCraszy %>% 
  tidy()


jjSplit %>% 
  ggplot(aes(x = jj, y = V2)) +
  geom_boxplot()
```

This cell provides statistically significant evidence that V2 is a terrible predictor of whether or not a language is studied in the source paper. OR, a really good one! Hard to say. The next cell compares with the other Vs
```{r}
jjV2 <- glm(jj ~ V2, family = "binomial", data = jjSplit)
summary(jjV2)
exp(4.55208)
```


```{r}
jjV2 <- glm(jj ~ V1, family = "binomial", data = jjSplit)
summary(jjV2)
exp(1.37210) / (exp(1.37210) + 1)
```



What's Miao up to? (we don't have hmong)
```{r}
all_data %>% 
  filter(language == "Miao") %>% 
  ggplot(aes(x = phonation, y = V3, color = tone_contour)) +
  geom_boxplot()

all_data %>% 
  filter(language == "Miao") %>% 
  ggplot(aes(x = V3, color = phonation)) +
  geom_density()
```

Tbh, we should make a barplot of Vx for phonation by language, mirroring our plots from earlier.
```{r}
all_data %>% 
  ggplot(aes(color = phonation, y = V1)) +
  geom_boxplot() +
  facet_wrap(~language)

all_data %>% 
  ggplot(aes(x = V2, color = phonation)) +
  geom_boxplot() +
  facet_wrap(~language)

all_data %>% 
  ggplot(aes(x = V3, color = phonation)) +
  geom_boxplot() +
  facet_wrap(~language)

all_data %>% 
  ggplot(aes(x = V4, color = phonation)) +
  geom_boxplot() +
  facet_wrap(~language)
```



```{r}
all_data %>% 
  group_by(language) %>% 
  count() %>% 
  mutate(perc = n / 4405)
```

```{r}
572 +196			+1178		+	1164		+	1295
```


